\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{url}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows.meta,shapes.geometric,fit,backgrounds}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Order-2 Co-occurrence TF-IDF for Interaction-Free Fragrance Dupe Retrieval: A Non-Circular Study}

\author{\IEEEauthorblockN{Azam Azri}
\IEEEauthorblockA{\textit{Master's Program in Informatics} \\
\textit{Affiliation (to be completed)}\\
Yogyakarta, Indonesia \\
azamazriahmad@mail.ugm.ac.id}
}

\maketitle

\begin{abstract}
Content-based perfume recommenders predominantly rank candidates by order-one
accord similarity, such as cosine or Jaccard over note sets. Whether modeling the
co-occurrence of accords improves retrieval has not been tested under a leakage-free
protocol, and the prevalent catalogs carry no user interactions, which rules out
collaborative and knowledge-graph recommenders that require an interaction signal.
This work studies interaction-free fragrance dupe retrieval: given a global perfume,
retrieve the local product that imitates it, with the held-out inspired-by edge as
ground truth. A parameter-free matcher is proposed that augments accord TF-IDF with
accord-pair (order-two) tokens; its cosine score decomposes additively into
order-one and order-two terms and yields faithful, auditable co-occurrence paths for
explanation. Evaluation uses 340 products and 209 queries under leave-one-out
ranking, with a three-source firewall whose query accords are independently verified
from Fragrantica. Against twelve comparison methods spanning marginal similarity,
neural embeddings, perceptual-taxonomy transport, and learned models, the proposed
method attains the best mean reciprocal rank (MRR 0.496) and beats the TF-IDF baseline
(0.454) by a modest but robust margin (delta-MRR +0.042, 95\% CI [+0.019, +0.067],
Wilcoxon p = 8.7e-8); order-two terms contribute 81.3\% of the top-ranked score.
The effect is honestly modest, and limitations are discussed.
\end{abstract}

\begin{IEEEkeywords}
recommender systems, content-based retrieval, co-occurrence, TF-IDF, explainability,
fragrance, non-circular evaluation
\end{IEEEkeywords}

\section{Introduction}
Selecting a fragrance ``dupe'' --- an affordable local product engineered to imitate
the scent of a well-known global perfume --- is a common consumer task and a natural
content-based retrieval problem. Each product is described by a small set of
olfactory \emph{accords} (e.g., \textit{amber}, \textit{woody}, \textit{warm spicy}),
and a dupe is expected to share much of the accord profile of the global perfume it
imitates. Existing perfume recommenders rank candidates almost exclusively by
order-one accord similarity, typically cosine over term frequency--inverse document
frequency (TF-IDF) vectors or Jaccard over accord sets \cite{r23,r24,r28}. Such marginal representations treat accords
independently and discard the structure in which accords co-occur.

A second constraint is decisive in practice: many real product catalogs record only
content (accord lists and family labels) and carry \emph{no} user interactions or
ratings. This excludes by construction the interaction-driven recommenders that
dominate the higher-order and knowledge-graph literature --- collaborative filtering,
LightGCN, KGIN, and KGAT \cite{r20} --- because they require a user--item signal the
data does not contain. Methods that do exploit item co-occurrence and higher-order
structure report strong gains, but only in interaction-based settings such as
session or multi-behavior recommendation \cite{r1,r2,r3,r4,r5}. Whether order-two
accord co-occurrence helps in a purely content-based, interaction-free regime, and
whether it does so under an evaluation that cannot leak the label, remains open.

A third assumption pervades adjacent fields: that injecting perceptual or learned
\emph{structure} aids retrieval. Perceptual odor science organizes accords on sensory
wheels and perceptual maps \cite{r10,r12,r13}, and a large body of work assumes such
geometry should help. Yet evidence from small and imbalanced datasets repeatedly
shows that simple baselines match or beat flexible models that overfit
\cite{r14,r15,r16,r17}. This tension has not been examined for interaction-free
fragrance retrieval.

This paper addresses these gaps with a deliberately simple, parameter-free method and
a rigorous, non-circular protocol. Accords and accord-pairs (unigrams and bigrams of
a co-occurrence graph) are weighted by inverse document frequency and compared by
cosine; the score decomposes additively into an order-one (marginal) term and an
order-two (co-occurrence) term, and the shared accord-pairs form auditable
explanation paths grouped by fragrance-wheel super-family. The matcher is intentionally
free of trained parameters: added capacity is shown empirically to overfit. The
contribution is a \emph{finding and a protocol}, not a new model, calibrated to a
moderate, applied scope.

The main contributions are:
\begin{itemize}
\item \textbf{Task and protocol.} We formalize interaction-free dupe retrieval and a
non-circular evaluation with a three-source firewall (local item accords, externally
sourced query accords verified from Fragrantica, and held-out inspired-by labels), and
we make explicit why interaction-based recommenders (KGAT, LightGCN, KGIN) cannot be
compared on this data.
\item \textbf{Method.} An order-two co-occurrence TF-IDF matcher whose cosine score
decomposes into order-one and order-two terms, paired with faithful-by-construction
co-occurrence explanation paths for a downstream explainability layer.
\item \textbf{Finding.} A first non-circular demonstration that order-two
co-occurrence ranks first in a fifteen-method benchmark, beating all twelve comparators
across four paradigms --- marginal similarity, neural embeddings, perceptual-taxonomy
transport, and learned models --- while the two proposed variants do not improve on it.
The result is reported with honest caveats: the gain over the TF-IDF baseline is modest
(+0.042 MRR) but robust and significant; the Sentence-BERT loss is partly attributable
to query-product text asymmetry; and the moderate learned methods only match, rather
than fall far below, the baseline.
\item \textbf{Reproducibility.} A complete, deterministic benchmark of fifteen
methods with paired significance testing and bootstrap confidence intervals.
\end{itemize}

The remainder of the paper reviews related work; formalizes the problem and the
non-circular firewall; presents the proposed method; describes the experimental setup;
reports results; discusses them; and states limitations before concluding.

\section{Related Work}\label{sec:related}

\subsection{Content-based perfume recommendation}
Perfume recommenders are overwhelmingly content-based and order-one. Lutan
\cite{r23} surveys the field and identifies subjectivity and sparse sensory data as
core obstacles. Nurmuthia \textit{et al.} \cite{r24} rank perfumes by cosine and
Jaccard similarity over note descriptions, and Fannisa \textit{et al.} \cite{r28}
report that a TF-IDF content-based filter outperforms a Word2Vec variant for perfume
selection. These systems treat accords as independent terms; none tests whether
modeling accord \emph{co-occurrence} improves retrieval, and none does so under a
protocol that prevents the label from leaking into the features. The present work
targets exactly this gap.

\subsection{Co-occurrence and higher-order recommendation}
Outside the fragrance domain, co-occurrence and higher-order structure are known to
help. Higher-order graph neural networks \cite{r1}, item co-occurrence graphs for
session-based recommendation \cite{r2}, graph-based feature crossing \cite{r3},
multi-modal session models that look beyond raw co-occurrence \cite{r4}, and the use
of negative co-occurrence signals \cite{r5} all improve accuracy. Crucially, every one
of these methods consumes a user--item or session interaction signal. Our setting is
interaction-free and content-only, so these techniques cannot be transferred directly;
we instead lift co-occurrence into the content representation itself.

\subsection{Knowledge-graph and explainable recommendation}
Knowledge-graph recommenders such as KGAT \cite{r20} and reasoning- or path-based
explainable models \cite{r18,r19,r21} produce relational explanations, but they depend
on user--item interactions to learn entity embeddings and attention, and their paths
can be only loosely tied to the predicted score. Because the catalog studied here has
no interactions, KGAT, LightGCN, and KGIN are not applicable and are explicitly excluded
from comparison. The proposed method instead derives explanation paths directly from the
shared accord-pairs that produce the score, so the paths are discriminative (weighted by
inverse document frequency) and faithful by construction.

\subsection{Perceptual structure and optimal transport}
Olfactory science represents odors with sensory wheels and perceptual maps
\cite{r10,r11,r12,r13}, and a natural hypothesis is that imposing such perceptual
geometry should aid retrieval. Transport-based distances on trees and graphs provide a
principled way to compare distributions over such a structure \cite{r7,r8,r9,r9b}. We
operationalize this hypothesis as a tree-Wasserstein distance over the Edwards
fragrance wheel and test it directly; rather than assuming the structure helps, we
measure whether it does.

\subsection{Simple baselines on small, imbalanced data}
A recurring lesson across domains is that flexible, high-capacity models fail to beat
simple baselines when data are scarce or imbalanced: linear baselines remain
competitive for gene-perturbation prediction \cite{r14}, and overfitting under class
imbalance is well documented for small medical datasets \cite{r15,r16,r17}. Item
cold-start recommenders likewise lean on content rather than capacity \cite{r25,r26,r27}.
These results motivate our parameter-free design and frame the expectation, later
confirmed, that learned and over-smoothed alternatives do not surpass a simple
co-occurrence matcher on a sparse fragrance catalog.

\subsection{Positioning}
The intersection this work occupies --- interaction-free, non-circular, order-two
co-occurrence for fragrance retrieval, used to test rather than assume the benefit of
perceptual, neural, and learned structure --- is, to our knowledge, unaddressed by the
literature above.

\section{Problem Formulation}\label{sec:problem}

\subsection{Interaction-free dupe retrieval}
Let $\mathcal{P}=\{p_1,\dots,p_N\}$ be the catalog of local products, with $N=340$.
Each product $p$ carries a set of olfactory accords $A(p)\subseteq\mathcal{V}$ and a
local family label, where $\mathcal{V}$ is the accord vocabulary. Let $\mathcal{Q}$ be
the set of query perfumes (global references); each query $q$ carries accords $A(q)$
and a global family. The dupe relation defines, for each query, a gold set
\begin{equation}
g(q)=\{\,p\in\mathcal{P}\;:\;\textit{inspired\_by}(p)=q\,\}, \label{eq:gold}
\end{equation}
the products explicitly engineered to imitate $q$. A retrieval method assigns a score
$s(q,p)$ to every product and ranks the entire catalog; quality is measured by where the
gold product falls in that ranking, using the metrics and protocol defined later. Of the $340$ products,
$243$ carry a dupe label and $97$ are unlabeled originals that remain in the pool as
genuine distractors; $209$ queries have at least one labeled dupe and form the
evaluation set. Local and global accord vocabularies share $56$ accords.

The deployed system and the evaluation share an \emph{identical} scoring engine; they
differ only in the query source (free user text or a global perfume) and in whether a
gold answer exists. A global perfume is never returned as output: the pool is the
local catalog.

\subsection{A non-circular firewall}
The central methodological risk is circularity: if the query features were copied from
the very products they are meant to retrieve, any accord overlap would be a tautology.
We guard against this with a three-source separation (Table~\ref{tab:firewall}). Query
accords are sourced independently from Fragrantica---$264$ of $266$ \texttt{source\_url}
entries resolve to perfume-specific Fragrantica pages---rather than back-filled from the
local catalog, so the benchmark is non-circular by construction.

\begin{table}[htbp]
\caption{Three-source firewall for non-circular evaluation}
\begin{center}
\begin{tabular}{lll}
\toprule
\textbf{Component} & \textbf{Source} & \textbf{Independent of} \\
\midrule
Item features  & local catalog accords        & the label \\
Query features & Fragrantica accords (external) & local catalog \& label \\
Label          & held-out \textit{inspired\_by} edge & accord similarity \\
\bottomrule
\end{tabular}
\label{tab:firewall}
\end{center}
\end{table}

A leakage audit further removes identity-bearing text before any text-based method sees
it: the \texttt{interpreted\_as} field equals the global perfume name and is never
exposed, and a distinctive token of a product's own global name appears in the free-text
\texttt{meaning} of $32$ of $340$ products; these tokens are stripped prior to embedding.

\subsection{Why interaction-based recommenders are out of scope}
Collaborative and knowledge-graph recommenders---including LightGCN, KGIN, and KGAT
\cite{r20}---take as input a user--item interaction matrix $R\in\{0,1\}^{U\times I}$ and
learn user and item embeddings from it. The catalog studied here contains no users and
no interactions ($U=\varnothing$), so $R$ is undefined and these models cannot be
instantiated, let alone compared. This is a property of the data, not a choice of
convenience; we therefore restrict the comparison to content-only methods and state the
exclusion explicitly rather than reporting vacuous numbers.

\subsection{Validity of the proxy}
The dupe task measures \emph{perceptual} match, not user satisfaction, and results should
be read as such. Because a dupe is deliberately formulated to smell like its target,
accord overlap between a query and its gold product is high (about $86\%$ of a dupe's
accords are contained in the query's accord list). This overlap is a genuine signal
rather than a construction artifact, and it explains why even a strong method improves
only modestly over the marginal baseline.

\section{Proposed Method}\label{sec:method}
The proposed matcher represents each fragrance not only by which accords it contains
but by which accords \emph{co-occur} in it, weights both by rarity, and compares two
fragrances by a single cosine that splits cleanly into a marginal term and a
co-occurrence term. It has no trained parameters. Fig.~\ref{fig:arch} summarizes the
pipeline.

\subsection{Co-occurrence representation}
For a fragrance $f$ with accord set $A(f)$, define its accord co-occurrence graph
$G_f=(A(f),E_f)$ whose edges are the unordered accord pairs
\begin{equation}
E_f=\{(a,b)\;:\;a,b\in A(f),\ a<b\}. \label{eq:edges}
\end{equation}
The token set of $f$ is the union of its accords (unigrams) and its accord pairs
(bigrams),
\begin{equation}
T(f)=A(f)\,\cup\,E_f. \label{eq:tokens}
\end{equation}

\subsection{Rarity weighting and normalization}
Tokens are weighted by inverse document frequency over the catalog of $N$ products.
With document frequency $\mathrm{df}(t)=\lvert\{f:t\in T(f)\}\rvert$,
\begin{equation}
\mathrm{idf}(t)=\log\!\frac{1+N}{1+\mathrm{df}(t)}+1. \label{eq:idf}
\end{equation}
Rare signature pairs receive a high weight, whereas ubiquitous hub accords (e.g.,
\textit{woody}, \textit{citrus}) receive a low weight; the hub penalty is therefore
automatic and parameter-free. Each fragrance becomes a sparse vector
\begin{equation}
v_f[t]=
\begin{cases}
\mathrm{idf}(t) & \text{if } t\in T(f),\\
0 & \text{otherwise,}
\end{cases}
\label{eq:vector}
\end{equation}
which is then $L_2$-normalized, $v_f\leftarrow v_f/\lVert v_f\rVert_2$.

\subsection{Similarity and additive decomposition}
The score between a query $q$ and a product $p$ is the cosine of their token vectors,
which separates exactly into an order-one (marginal) and an order-two (co-occurrence)
contribution:
\begin{equation}
s(q,p)=\frac{S_1(q,p)+S_2(q,p)}{\lVert v_q\rVert\,\lVert v_p\rVert}, \label{eq:score}
\end{equation}
\begin{align}
S_1(q,p)&=\sum_{a\in A(q)\cap A(p)}\mathrm{idf}(a)^2,\label{eq:s1}\\
S_2(q,p)&=\sum_{e\in E_q\cap E_p}\mathrm{idf}(e)^2.\label{eq:terms}
\end{align}
Here $S_1$ rewards shared accords and $S_2$ rewards shared accord \emph{pairs}; because
both blocks share one normalizer, the two terms add up to the full score. Empirically,
the order-two term $S_2$ accounts for $81.3\%$ of the top-ranked score, confirming that
co-occurrence, not marginal overlap, drives retrieval. Ranking the $340$ products by
$s(q,p)$ in descending order and taking the three highest yields the Top-3 output.

\subsection{Explanation paths}
Because the score is a sum over shared tokens, every recommendation is explained by the
same quantities that produced it. For each Top-3 product, the shared accord pairs
$E_q\cap E_p$ are emitted as co-occurrence \emph{paths}, each carrying its weight
$\mathrm{idf}(e)^2$ and the Edwards fragrance-wheel super-family \cite{r10} of its two
accords (or \textit{cross-family} when they differ); shared single accords are emitted
as node paths. The resulting \texttt{kg\_paths} are auditable and faithful by
construction---they are not a post-hoc rationalization but the score decomposition
itself---and serve a downstream explainability layer.

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  font=\footnotesize,
  box/.style={draw, rounded corners, align=center, text width=0.80\linewidth,
              inner sep=4pt, minimum height=6.5mm},
  hbox/.style={draw, dashed, rounded corners, align=center, text width=0.80\linewidth,
               inner sep=4pt},
  arr/.style={-{Latex[length=2mm]}, thick}]
\node[box] (q) {Query: accords $A(q)$ + global family};
\node[box, below=3.5mm of q] (g) {Co-occurrence tokens $T(q)=A(q)\cup E_q$, IDF-weighted~$\star$};
\node[box, below=3.5mm of g] (m) {Parameter-free matcher $s(q,p)=\langle v_q,v_p\rangle$ (order-1 $+$ order-2)};
\node[box, below=3.5mm of m] (r) {Rank 340 products $\rightarrow$ Top-3};
\node[box, below=3.5mm of r] (k) {\texttt{kg\_paths}: shared pairs grouped by wheel super-family~$\star$};
\draw[arr] (q)--(g); \draw[arr] (g)--(m); \draw[arr] (m)--(r); \draw[arr] (r)--(k);
\node[hbox, below=4mm of k] (h) {Non-circular harness~$\star$: leave-one-out, leakage firewall, 15-method ladder, Wilcoxon + bootstrap};
\draw[arr, dashed] (k)--(h);
\end{tikzpicture}
\caption{Framework overview. A query is turned into an IDF-weighted co-occurrence token
vector, matched against the $340$ products by a parameter-free cosine, and the Top-3 are
returned with auditable \texttt{kg\_paths}. The whole pipeline is evaluated by a
non-circular harness. $\star$ marks the three novelty points.}
\label{fig:arch}
\end{figure}

\subsection{Design rationale}
The matcher is deliberately parameter-free. On a catalog this sparse---$209$ queries,
one relevant product each---added capacity overfits, as the experiments confirm: a
learning-to-rank fusion does not significantly beat the bare cosine, and high-dimensional
learned variants collapse, as reported in the results. Simplicity is thus a design
decision grounded in the data regime, not an omission.

\section{Experimental Setup}\label{sec:setup}

\subsection{Dataset and provenance}
The catalog contains $340$ local products; $243$ carry a dupe label and $97$ are
unlabeled originals retained as distractors. After joining each labeled product to its
global perfume, $209$ queries have at least one labeled dupe and form the leave-one-out
evaluation set. Local and global vocabularies share $56$ accords, drawn from $17$ local
and $49$ global families. Accord lists are parsed by splitting on commas and semicolons,
lower-casing, and trimming. Crucially, query accords are taken from the global reference
table whose entries are independently sourced: $264$ of $266$ \texttt{source\_url} values
resolve to perfume-specific Fragrantica pages, so query features are not back-filled from
the catalog they retrieve.

\subsection{Methods}
We evaluate fifteen methods organized into three tiers (Table~\ref{tab:methods}). Tier~1
collects established baselines: marginal accord similarity (Jaccard, TF-IDF cosine, and
BM25) and neural embeddings (a multilingual Sentence-BERT \cite{r22} over the textual
fields, a Word2Vec model over accord sequences, and node2vec over the accord
co-occurrence graph). Tier~2 collects structured or learned comparators expected to test
whether added structure helps: a tree-Wasserstein distance over the Edwards fragrance
wheel \cite{r10}, a positive pointwise mutual information embedding with truncated SVD, a
signature-subgraph learning-to-rank model, a high-dimensional per-bigram salience
logistic model, a low-rank bilinear metric, and a gradient-boosting fusion. Tier~3 is the
proposed family: the order-two matcher (P1), a learning-to-rank fusion of its components
(P2), and a hub-discriminative IDF ablation (P3). B2 (TF-IDF cosine) is the primary
marginal baseline.

\begin{table}[htbp]
\caption{The fifteen-method comparison ladder}
\begin{center}
\begin{tabular}{llp{0.30\linewidth}}
\toprule
\textbf{ID} & \textbf{Paradigm} & \textbf{Method} \\
\midrule
B1 & marginal      & Jaccard over accord sets \\
B2 & marginal      & TF-IDF cosine (primary baseline) \\
B3 & marginal      & BM25 over accord tokens \\
B4 & neural        & Sentence-BERT over text \\
B5 & neural        & Word2Vec accord embeddings \\
B6 & neural        & node2vec on co-occurrence graph \\
A1 & perceptual    & Edwards-wheel tree-Wasserstein \\
A2 & learned       & PPMI + truncated SVD \\
A3 & learned       & signature-subgraph LTR \\
A4 & learned       & per-bigram salience logistic \\
A5 & learned       & low-rank bilinear metric \\
A6 & learned       & gradient-boosting fusion \\
P1 & \textbf{proposed} & order-2 co-occurrence TF-IDF \\
P2 & proposed      & P1 + LTR fusion \\
P3 & proposed      & P1 + hub-discriminative IDF \\
\bottomrule
\end{tabular}
\label{tab:methods}
\end{center}
\end{table}

\subsection{Metrics}
With one relevant product per query, we report mean reciprocal rank (MRR) and Hits@$k$,
\begin{align}
\mathrm{MRR}&=\frac{1}{|\mathcal{Q}|}\sum_{q\in\mathcal{Q}}\frac{1}{r_q},\label{eq:mrr}\\
\mathrm{Hits}@k&=\frac{1}{|\mathcal{Q}|}\sum_{q\in\mathcal{Q}}\mathbf{1}[\,r_q\le k\,],\label{eq:hits}
\end{align}
where $r_q$ is the rank of the best (smallest-rank) gold product for query $q$, and
$k\in\{1,3\}$. Ties in score are resolved by the expected reciprocal rank under uniform
random tie-breaking, which neither rewards nor penalizes tie-heavy methods.

\subsection{Protocol and significance}
Every method ranks the full pool of $340$ products. Supervised methods (A3--A6, P2) are
scored out-of-fold with $5$-fold \emph{GroupKFold} grouped by query, so no query appears
in both training and test. Deterministic methods are run once; stochastic methods (A2,
A5, B5, B6, and the fold-shuffled learning-to-rank models) are run over $5$ seeds and
reported as mean$\pm$standard deviation. Statistical significance against the proposed
method uses the Wilcoxon signed-rank test paired across queries on the reciprocal ranks;
because deterministic methods have no seed variance, significance is computed across
queries rather than across seeds. Confidence intervals for the difference in MRR use
$10{,}000$ bootstrap resamples over queries. For the text-based method, the leakage audit
of Section~\ref{sec:problem} is applied before embedding. The pipeline is implemented in
Python with fixed seeds for full reproducibility; only the optional Sentence-BERT baseline
requires a pretrained model download.

\section{Results}\label{sec:results}

\subsection{Retrieval accuracy}
Table~\ref{tab:results} reports MRR, Hits@1, and Hits@3 for all fifteen methods. The
proposed order-two matcher P1 reaches MRR $0.496$, the top score among the twelve
comparison methods; the next best comparator, the gradient-boosting fusion A6, trails at
$0.457$, and the primary TF-IDF baseline B2 at $0.454$. The learning-to-rank fusion P2 is
numerically marginally higher ($0.500$) but, as shown below, is statistically
indistinguishable from P1; we therefore treat the parameter-free P1 as the method of
record and P2 as an ablation. The remaining paradigms fall clearly behind: neural
embeddings (B6 $0.340$, B4 $0.272$, B5 $0.185$), the perceptual-taxonomy transport (A1
$0.284$), and the high-dimensional learned models (A5 $0.150$, A4 $0.139$) are all well
below the marginal baseline, while the moderate learned models (A2 $0.444$, A6 $0.457$)
only reach it.

\begin{table}[t]
\caption{Retrieval accuracy of all fifteen methods (mean over 5 seeds for stochastic methods)}
\begin{center}
\begin{tabular}{llccc}
\toprule
\textbf{ID} & \textbf{Tier} & \textbf{MRR} & \textbf{Hits@1} & \textbf{Hits@3} \\
\midrule
\textbf{P1} & proposed   & \textbf{0.496} & \textbf{0.378} & \textbf{0.562} \\
P2          & proposed   & 0.500          & 0.379          & 0.580 \\
P3          & proposed   & 0.448          & 0.335          & 0.491 \\
\midrule
B1 & marginal   & 0.428 & 0.303 & 0.487 \\
B2 & marginal   & 0.454 & 0.335 & 0.507 \\
B3 & marginal   & 0.388 & 0.278 & 0.433 \\
B4 & neural     & 0.272 & 0.163 & 0.311 \\
B5 & neural     & 0.185 & 0.110 & 0.182 \\
B6 & neural     & 0.340 & 0.233 & 0.371 \\
A1 & perceptual & 0.284 & 0.174 & 0.306 \\
A2 & learned    & 0.444 & 0.343 & 0.498 \\
A3 & learned    & 0.433 & 0.303 & 0.500 \\
A4 & learned    & 0.139 & 0.060 & 0.145 \\
A5 & learned    & 0.150 & 0.072 & 0.150 \\
A6 & learned    & 0.457 & 0.325 & 0.533 \\
\bottomrule
\end{tabular}
\label{tab:results}
\end{center}
\end{table}

\subsection{Significance}
Table~\ref{tab:sig} pairs P1 against every other method across queries. P1 has a
positive, significant advantage over all twelve comparators. The headline comparison
against the marginal baseline B2 is modest but robust: $\Delta\mathrm{MRR}=+0.042$, with a
$95\%$ bootstrap confidence interval of $[+0.019,+0.067]$ and Wilcoxon
$p=8.7\times10^{-8}$. Margins are far larger over the neural and high-dimensional learned
methods (e.g., $+0.225$ over B4, $+0.294$ over B5, $+0.367$ over A4). Against the moderate
learned models the gain is small yet still significant ($+0.054$ over A2, $+0.052$ over
A6), which is why we describe them as matching, not surpassing, the baseline rather than
failing outright. The fusion variant P2 does not significantly differ from P1
($\Delta\mathrm{MRR}=-0.005$, $p=0.18$), confirming that added learning capacity is
unnecessary.

\begin{table}[t]
\caption{P1 versus each method: paired Wilcoxon test on reciprocal rank and bootstrap 95\% CI for $\Delta$MRR}
\begin{center}
\begin{tabular}{lccc}
\toprule
\textbf{vs.} & \textbf{$\Delta$MRR} & \textbf{95\% CI} & \textbf{Wilcoxon $p$} \\
\midrule
B1 & $+0.069$ & $[+0.040,+0.100]$ & $6.6\times10^{-3}$ \\
B2 & $+0.042$ & $[+0.019,+0.067]$ & $8.7\times10^{-8}$ \\
B3 & $+0.108$ & $[+0.076,+0.143]$ & $8.3\times10^{-12}$ \\
B4 & $+0.225$ & $[+0.166,+0.283]$ & $1.6\times10^{-11}$ \\
B5 & $+0.294$ & $[+0.233,+0.354]$ & $2.0\times10^{-16}$ \\
B6 & $+0.181$ & $[+0.131,+0.233]$ & $2.7\times10^{-11}$ \\
A1 & $+0.213$ & $[+0.158,+0.268]$ & $3.9\times10^{-13}$ \\
A2 & $+0.054$ & $[+0.011,+0.099]$ & $3.9\times10^{-3}$ \\
A3 & $+0.066$ & $[+0.039,+0.093]$ & $5.7\times10^{-8}$ \\
A4 & $+0.367$ & $[+0.309,+0.426]$ & $2.7\times10^{-21}$ \\
A5 & $+0.332$ & $[+0.275,+0.391]$ & $2.5\times10^{-21}$ \\
A6 & $+0.052$ & $[+0.017,+0.087]$ & $2.3\times10^{-2}$ \\
P2 & $-0.005$ & $[-0.020,+0.011]$ & $0.18$ (n.s.) \\
P3 & $+0.049$ & $[+0.025,+0.073]$ & $6.2\times10^{-10}$ \\
\bottomrule
\end{tabular}
\label{tab:sig}
\end{center}
\end{table}

\subsection{Where the signal comes from}
Decomposing the P1 score by~\eqref{eq:score}--\eqref{eq:terms} shows that the order-two
term $S_2$ contributes, on average, $81.3\%$ of the top-ranked score, against $18.7\%$ for
the order-one term $S_1$. The advantage of P1 is therefore not a re-weighting of marginal
similarity but a genuinely second-order effect: shared rare accord \emph{pairs}, not
shared individual accords, separate the correct dupe from the distractors.

\section{Discussion}\label{sec:discussion}
The results answer the two primary research questions of this study and qualify each
answer with the caveats the data demand.

\subsection{RQ1: does order-two co-occurrence beat marginal similarity?}
Yes, but modestly. The proposed matcher P1 ranks first among all twelve comparison
methods and improves on the marginal TF-IDF baseline B2 by
$\Delta\mathrm{MRR}=+0.042$, an effect that is small in absolute terms yet robust: the
$95\%$ bootstrap confidence interval $[+0.019,+0.067]$ excludes zero, and the paired
Wilcoxon test is decisive ($p=8.7\times10^{-8}$). The decomposition of
Section~\ref{sec:results} explains why a small headline gain is nonetheless a genuine
second-order effect rather than baseline noise: order-two terms supply $81.3\%$ of the
top-ranked score, so it is shared rare accord \emph{pairs}---not shared individual
accords---that lift the correct dupe above the distractors. The reason the improvement
cannot be large is structural and was anticipated in
Section~\ref{sec:problem}: a dupe is engineered to smell like its target, so roughly
$86\%$ of a dupe's accords already appear in the query, leaving the marginal baseline a
high floor and the co-occurrence term only a narrow margin to exploit. The honest
reading is that order-two structure helps reliably, not dramatically.

\subsection{RQ2: do perceptual, neural, or learned structures help?}
No structure surpasses the simple co-occurrence matcher, but the comparators fail at two
clearly different magnitudes, and conflating them would overstate the result. The first
group fails decisively. The perceptual-taxonomy transport A1 ($0.284$), the neural
embeddings B5 ($0.185$), B6 ($0.340$), and B4 ($0.272$), and the high-dimensional learned
models A4 ($0.139$) and A5 ($0.150$) all fall well below even the marginal baseline, with
large and highly significant gaps to P1 (e.g., $+0.367$ over A4, $+0.294$ over B5,
$p<10^{-16}$). These methods share a common mechanism of failure: each smooths or
re-embeds the discrete accord-pair signal into a continuous latent space, and on a
catalog with a single relevant product per query that smoothing erases exactly the rare,
discriminative co-occurrences that the exact-match cosine preserves. The wheel transport
averages over a perceptual geometry the data do not reward; the embeddings dissolve
pair identity into dense vectors; and the high-capacity learned models overfit a severe
one-positive-per-query imbalance. This is the empirical core of the finding: added
representational capacity does not help here---it hurts.

The second group is where the claim must be softened. The two moderate learned methods,
PPMI with truncated SVD (A2, $0.444$) and the gradient-boosting fusion (A6, $0.457$),
land essentially on top of the marginal baseline B2 ($0.454$). They do not collapse like
A4 and A5; they simply fail to exceed the baseline. P1 still beats both by a small but
significant margin ($+0.054$ over A2, $+0.052$ over A6), so the correct statement is that
moderate learned structure \emph{matches} the marginal baseline without surpassing it,
rather than that learned methods fail outright. RQ2 is thus answered with a graded
conclusion: high-dimensional and perceptual structure overfit and lose decisively, while
moderate learned structure only reaches the baseline---neither buys the second-order
advantage that the parameter-free co-occurrence matcher obtains for free.

\subsection{The Sentence-BERT result is partly an artifact of text asymmetry}
The weak performance of the multilingual Sentence-BERT baseline B4 ($0.272$) should not
be read as evidence that semantic text matching is inherently useless for this task. The
query and product text are asymmetric by construction: product descriptions are rich
Indonesian prose, whereas the externally sourced queries carry little more than an accord
list, so the two sides of every comparison are drawn from different text distributions
before any leakage stripping is applied. A sentence encoder is penalized by this
mismatch independently of its semantic quality. We therefore attribute the B4 result
jointly to the genuine advantage of exact accord-pair matching \emph{and} to query
text being far sparser than product text, and we refrain from the stronger claim that
neural semantics cannot contribute under a more symmetric text regime.

\subsection{Why the simplest method wins: design, not omission}
That the most capable comparators lose while the parameter-free P1 wins is consistent
with a recurring lesson on small, imbalanced data, where flexible models overfit and
simple baselines hold \cite{r14,r15,r16,r17}. Two internal controls confirm the point
rather than merely asserting it. First, the learning-to-rank fusion P2 ($0.500$) is
statistically indistinguishable from the bare cosine P1 ($\Delta\mathrm{MRR}=-0.005$,
$p=0.18$): adding trained weights on top of the same features buys nothing, so we report
the parameter-free P1 as the method of record. Second, the high-dimensional learned
variants A4 and A5 do not merely fail to help but collapse to near the bottom of the
table, the signature of overfitting under one-positive-per-query supervision. The
simplicity of the matcher is therefore a deliberate design choice grounded in the data
regime, not an unexamined limitation.

\subsection{Faithful explanation paths}
Because the cosine score is a sum over shared tokens, the same accord-pairs that produce
a recommendation are emitted as its explanation. For each Top-3 product the matcher
exports \texttt{kg\_paths}: the shared accord-pairs $E_q\cap E_p$, each annotated with
its weight $\mathrm{idf}(e)^2$ and the Edwards-wheel super-family of its endpoints (or
\textit{cross-family}), together with the shared single accords. For the query
\textit{1~Million} the gold product surfaces at rank one supported by signature pairs
such as \textit{amber--cinnamon} and \textit{cinnamon--warm spicy}, each carrying its
exact contribution to the score. These paths are faithful by construction---they are the
score decomposition itself, not a post-hoc rationalization---and discriminative because
inverse document frequency down-weights ubiquitous hubs. We position them as an auditable
deliverable for a downstream explainability layer; a counterfactual edge-ablation study
that would quantify their faithfulness beyond the order-one/order-two decomposition is
left to that collaboration and is not claimed here.

\section{Limitations}\label{sec:limitations}
The scope of the contribution and the data regime impose several limitations, which we
state plainly so that the result is not read more strongly than it warrants.

\begin{itemize}
\item \textbf{Binary accords.} Accords are modeled as presence/absence; the catalog
records no per-accord intensity. Two products with identical accord sets are therefore
indistinguishable to the matcher, and an intensity-weighted co-occurrence representation
cannot be tested because the signal is absent from the source data.
\item \textbf{Small evaluation set and limited power.} With $209$ queries and a single
relevant product each, statistical power is bounded; we report confidence intervals and
paired tests precisely for this reason. The headline effect over the marginal baseline is
correspondingly modest ($\Delta\mathrm{MRR}=+0.042$), and the high accord overlap inherent
to the dupe task (Section~\ref{sec:problem}) caps how large any second-order gain can be.
\item \textbf{Proxy validity.} The dupe relation measures \emph{perceptual} imitation,
not user satisfaction or purchase behavior. Because a dupe is deliberately formulated to
smell like its target, query--gold accord overlap is high by construction; results should
be read as a retrieval proxy rather than a measure of recommendation utility.
\item \textbf{Scope of the novelty.} The contribution is a finding and a non-circular
protocol, not a new model. The matcher is parameter-free \emph{by design}: as
Section~\ref{sec:discussion} shows, added capacity overfits this data regime. Simplicity
is thus a deliberate choice, but it also means the method offers no mechanism to exploit
richer signals (intensity, text, interactions) should they become available.
\item \textbf{Text-asymmetry confound.} As discussed in Section~\ref{sec:discussion}, the
weak Sentence-BERT result is partly attributable to the asymmetry between sparse query
text and rich product prose; it is therefore not clean evidence that semantic matching is
useless, and a symmetric-text evaluation remains future work.
\item \textbf{Generalization.} All results come from a single proprietary catalog in one
fragrance market. Whether order-two co-occurrence retains its advantage on other catalogs,
domains, or larger vocabularies is untested, and external validity should not be assumed.
\end{itemize}

\section{Conclusion}\label{sec:conclusion}
This work studied interaction-free fragrance dupe retrieval and asked whether modeling
the co-occurrence of accords improves retrieval over the marginal similarity that
dominates perfume recommendation. The contribution is a finding and a protocol rather
than a new model. We formalized the task and built a non-circular evaluation---a
three-source firewall with externally verified query accords, a leakage audit, and a
fifteen-method comparison ladder---and we made explicit why interaction-driven
recommenders such as KGAT, LightGCN, and KGIN cannot be instantiated on a catalog with no
user interactions. Within this protocol, a deliberately parameter-free matcher that
augments accord TF-IDF with order-two accord-pair tokens ranks first among all fifteen
methods, beating every comparator across four paradigms---marginal similarity, neural
embeddings, perceptual-taxonomy transport, and learned models.

The result is reported with its caveats intact. The gain over the marginal TF-IDF
baseline is modest ($\Delta\mathrm{MRR}=+0.042$) yet robust and significant
($p=8.7\times10^{-8}$), and a score decomposition attributes $81.3\%$ of the top-ranked
score to the order-two term, confirming a genuinely second-order effect. The improvement
is bounded by the high accord overlap inherent to the dupe task; moderate learned methods
only match the baseline rather than fall far below it; the Sentence-BERT result is partly
a text-asymmetry artifact; and added learning capacity does not help, since a
learning-to-rank fusion is statistically indistinguishable from the bare cosine. Taken
together, the evidence supports the parameter-free design as a consequence of the sparse,
one-positive-per-query data regime, not an oversight.

Future work follows directly from the limitations. An intensity-weighted co-occurrence
representation could be tested if per-accord intensity becomes available; a symmetric-text
evaluation would isolate the semantic contribution of sentence encoders from the
query--product asymmetry; a counterfactual edge-ablation study, in collaboration with a
downstream explainability layer, would quantify the faithfulness of the exported
\texttt{kg\_paths} beyond the order-one/order-two decomposition reported here; and
replication on additional catalogs and domains would test external validity. The broader
methodological message is that a non-circular protocol can convert a plausible intuition
into a measured, honestly bounded finding.

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
